---
title: "Using QY_lm for Linear Regression"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using QY_lm for Linear Regression}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
# Introduction
The `QY_lm` function provides an alternative implementation of linear regression, 
mimicking the functionality of the base R function `lm()`. This function is designed to
be modular and serves as an educational tool to demonstrate the underlying principles 
of linear regression. 

In this vignette, we will demonstrate the usage of `QY_lm` and compare its performance 
and accuracy against the base R `lm()` function using simulated data.


```{r setup}
library(BIO625HW3)
```

# Example Usage
## Simulated Data
The following code generates a dataset with 100 observations, where `x` and `y` are independent normally distributed random variables. We fit the model `y ~ x` using `QY_lm`.

Let's create a small dataset and fit a model:

```{r}
set.seed(123)
data <- data.frame(x = rnorm(100), y = rnorm(100))
result <- QY_lm(data, y ~ x)
print(result$coefficients)
```

#Compare the results of `QY_lm` with the base R `lm` function to ensure the correctness of the implementation.


```{r}
# Fit a linear model using QY_lm
result <- QY_lm(data, y ~ x)
print(result$coefficients)

# Fit a linear model using lm
base_result <- lm(y ~ x, data = data)
print(coef(base_result))

# Compare the results
print(all.equal(result$coefficients, coef(base_result)))
```


```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


